DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-08-21 ase2017/paper.tex
articles

%The digital controllers synthesized by \tool are all stable using the MATLAB step response
%as a validation procedure, which means that our results are reliable for control engineers. 
The synthesized controllers are also confirmed to be safe outside of our model
representation using MATLAB, which means that our results are usable for control engineers. 
Given that the closed loop dynamics are convergent, 
the controller's safety can be checked by computing the initial state's infinity norm, i.e., 
the product between $l_{\infty}$ norm of initial states ($\vert\vert{x_{0}}\vert\vert_{\infty}=\max{x_{0}}$) 
and the $l_{1}$ norm of ($\vert\vert{\bar{A}}\vert\vert_{1}=\max\limits_{j}{\sum\limits_{i=1}^{m} \vert \bar{a}_{ij} \vert}$, 
where $\bar{A}=A-BK$). This is a conservative safety check, which is based on a sufficient condition~\cite{toscano2013structured}. 
An~alternative (but not conservative) approach is to unfold the system dynamics up to a given depth, 
with the initial state equal to its maximum value, compute the system input and output via the feedback matrix, 
and then check the state bounds.

>>>>

%The digital controllers synthesized by \tool are all stable using the MATLAB step response
%as a validation procedure, which means that our results are reliable for control engineers.

The synthesized controllers are also confirmed to be safe outside of our
model representation using MATLAB, which means that our results are usable
for control engineers.  Given that the closed loop dynamics are convergent,
the controller's safety can be checked by computing the initial state's
infinity norm, i.e., the product between the $l_{\infty}$ norm of the
initial states ($\vert\vert{x_{0}}\vert\vert_{\infty}=\max{x_{0}}$) and the
$l_{1}$ norm of
($\vert\vert{\bar{A}}\vert\vert_{1}=\max\limits_{j}{\sum\limits_{i=1}^{m}
\vert \bar{a}_{ij} \vert}$, where $\bar{A}=A-BK$).  This is a conservative
safety check, which is based on a sufficient
condition~\cite{toscano2013structured}.  An~alternative (but not
conservative) approach is to unfold the system dynamics up to a given depth,
with the initial state equal to its maximum value, compute the system input
and output via the feedback matrix, and then check the state bounds.
